Query Optimization for Dynamic Imputation

### 2017-03-01 paper/experiments.tex
paper: minor formatting & reference fix

Our first set of queries is on the CDC data (\Cref{fig:queries-cdc}).
\Cref{q1} calculates calculate the average cuff size for users based on their income data.
\Cref{q2} compares creatine levels for individuals with low, medium, and high incomes and above a certain weight.
\Cref{q3} extracts the average blood lead levels for children under 6 years of age.
\Cref{q4} calculates the average systolic blood pressure, by gender, for subjects with a body mass index indicating obesity. 
\Cref{q5} calculates the average waist circumference for subjects above a certain height and
weight.

@@

\begin{table*}
  \centering
  \begin{subtable}{\linewidth}
    \input{queries-cdc}
    \caption{Queries on CDC data}\label{fig:queries-cdc}
  \end{subtable}
  \par\medskip
  \begin{subtable}{\linewidth}
    \input{queries-fcc}
    \caption{Queries on freeCodeCamp data}\label{fig:queries-fcc}
  \end{subtable}
  \par\medskip
  \caption{Queries used in our experiments.}\label{fig:queries}
\end{table*}

@@

Each query was separately run 200 times in both settings and then results from the two approaches were
paired up and compared tuple-wise.  We average tuple-wise absolute percentage deviations
within each iteration of a query, and we report this value averaged over all iterations.  We
can see that optimizing for quality indeed reduces the SMAPE of query results.  In general, the SMAPE relative 
to the base-imputation approach is low in all cases --- between
\lowsmapealphazero{} and \highsmapealphaoneexacs{} percent ---, indicating that on-the-fly
imputation produces similar results to imputation at the base tables.

>>>>

Our first set of queries is on the CDC data (\Cref{fig:queries-cdc}).
\Cref{q1} calculates calculate the average cuff size for individuals based on their income data, with a constraint on height.
\Cref{q2} compares creatine levels for individuals with low, medium, and high incomes and above a certain weight.
\Cref{q3} extracts the average blood lead levels for children under 6 years of age.
\Cref{q4} calculates the average systolic blood pressure, by gender, for subjects with a body mass index indicating obesity. 
\Cref{q5} calculates the average waist circumference for subjects above a certain height and weight.

@@

\begin{table*}
  \todo{query parameter scaling}
  \centering
  \begin{subtable}{\linewidth}
    \input{queries-cdc}
    \caption{Queries on CDC data}\label{fig:queries-cdc}
  \end{subtable}
  \par\medskip
  \begin{subtable}{\linewidth}
    \input{queries-fcc}
    \caption{Queries on freeCodeCamp data}\label{fig:queries-fcc}
  \end{subtable}
  \par\medskip
  \caption{Queries used in our experiments.}\label{fig:queries}
\end{table*}

@@

Each query was separately run 200 times in both settings and then results from the two approaches were
paired up and compared tuple-wise.  We average tuple-wise absolute percentage deviations
within each iteration of a query, and we report this value averaged over all iterations.  We
can see that optimizing for quality indeed reduces the SMAPE of query results.  In general, the SMAPE relative 
to the base-imputation approach is low in all cases---between
\lowsmapealphazero{} and \highsmapealphaoneexacs{} percent---indicating that on-the-fly
imputation produces similar results to imputation at the base tables.
